
You can assign values to new objects using the "left arrow" `<- `. It's typed with a less-than sign `<` followed by a hyphen `-`. 
It's more officially known as the _assignment operator_. 

Let's create a droid! 
Try adding the code below to your R script to create an object called `droid`.

To run a line of code in your script, move the cursor to that line and press __CTRL+ENTER__.

## Assignment operator {-}

```{r names, eval=F}

# Create a new object
droid <- "bb8"

droid 
```

Now let's make a Wookie. He can be friends with the droid.

```{r names2, eval=F}
wookie <- "Chewbacca"

wookie

```

<br>

__Break some things__
```{r, error=T}
# To save text to a character object you need quotation marks: "text"

# Try this:
wookie <- Chewbacca
```


<div class="red-note" style="width: 93%;">
__ERROR__

Without quotes, R looks for an object called Chewbacca, and then lets you know that it couldn't find one. 
</div>

<br>

__Copy objects__
```{r duplicate, eval=F}
# To copy an object, assign it to a new name
wookie2 <- wookie


# Or overwrite an object with new "text"
wookie <- "Tarfful"
  
wookie


# Did this change the value stored in wookie2?
wookie2  

```

__Numbers!__

```{r nums, eval=F}

wookie_salary <- 500

# Let's give Chewbacca a raise $$
wookie_salary <- 500 * 2

# Print new salary value
wookie_salary

```
<br>

## Drop and remove data {-}

You can drop objects with the remove function `rm() `. Try it out on some of your wookies.

```{r, eval = F}

# Delete objects to clean-up your environment
rm(wookie)

rm(wookie2)

```

<div class="tip">
  
### <i class="fa fa-user-astronaut" aria-hidden="true" style="color: green"></i> Exercise! {-}

How can we get the `wookie` object back?

__HINT:__ _You are allowed to re-run code._
</div>


<br>

<details>
<summary class = "btn_code_blue"> **EXPLORE: ** Deleting data is okay </summary>
<div class="note">
<p>
Don't worry about deleting data or objects in R. You can always recreate them! When R loads your data it copies the contents and then cuts off any connection to the original data. So your original data remain safe and won't suffer any accidental changes. That means if something disappears or goes wrong in R, it's okay. We can reload the data using our R script. 

It's common to re-run an entire R script multiple times
</div>
</p></details>
